# Introduction {#intro}

The [note] sign is historically equal to the asterisks used by Aristarchus of Samothrace at the Mouseion at Alexandria. It was used for the critical editions of Homer's writings where it "marked a verse incorrectly repeated in another passage" and was used together with other signs such as the obelus.^[[L.D. Reynolds and N.G. Wilson](). *Scribes and Scholars: A guide to the Transmission of Greek and Latin Literature*. Oxford University Press, 1991, 3rd edition, ISBN 0-19-872146-3, p. 10-11] The London printer Richard Jugge is generally credited as the inventor of the footnote, first used in the Bishops' Bible of 1568.^[Chuck Zerby, *[The Devil's Details: A History of Footnotes]()*, 2007, ISBN 1931229058, p. 28 and *passim*]

Early printings of the Douay Bible used two closely spaced colons (actually squared four dot punctuation mark U+2E2C) to indicate a marginal note. (Source: [Wikipedia](https://en.wikipedia.org/wiki/Note_(typography)))


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.^[Here is fancy footnote.]

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

```{js, echo = FALSE, eval = FALSE}
  var sup = document.getElementsByClassName("ss-1");
    sup.onclick = function(event) {

      var footnoteText = this.parentElement.parentElement.getElementsByClassName('atlas-footnote-item');

      footnoteText[0].style.display = 'block';

      event.preventDefault();
    };
```
